---
title: "Untitled"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

# Probability
The country of Chile is divided administratively into 15 regions. The size of the country is 756,096 square kilometers. How big do you think the region of Atacama is? Let A_1 be the event that Atacama is less than 10,000 square kilometers. Let A_2 be the event that Atacama is between 10,000 and 50,000 square kilometers. Let A_3 be the event that Atacama is between 50,000 and 100,000 square kilometers. Let A_4 be the event that Atacama is more than 100,000 square kilometers. Assign probabilities to A_1,..., A_4.
Around 50.000 would be my bests guess.  

```{r}
756096/15
```

## Extra information
Atacama is the fourth largest of 15 regions. Using this information, revise your probabilities.  
The smallest region is the capital region, Santiago Metropolitan, which has an area of 15,403 square kilometers. Using this information, revise your probabilities.  

Event A_1, less than 10.000 sq km has now the probability of zero. 
